---
title: "FuelConsumption_Project"
author: "S18809"
date: "2023-10-03"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(janitor)
```
```{r}
library(skimr)
```

```{r}
library(tinytex)
```
```{r}
col_type <- "cccfdicfddddnff"
Co2_rating <- read_csv("../Data/MY2021 Fuel Consumption Ratings.csv",col_types = col_type)
head(Co2_rating)
```
```{r}
view(Co2_rating)
```

```{r}
Co2_rating <- Co2_rating %>%
  remove_empty(c("cols","rows"))
```

```{r}
view(Co2_rating)
```


```{r}
skim(Co2_rating)
```

```{r}
Co2_rating %>% 
  filter(is.na(Transmission)) %>%
  view()
```

```{r}
# Here keep the data data description in the csv files
data_des <- Co2_rating %>%
  filter(is.na(Transmission))
```

```{r}
Co2_rating <- Co2_rating %>%
  drop_na()
```

```{r}
glimpse(Co2_rating)
```
# Clean name the function 
# Clean_names function comming from janitor package
# case = "snake" , "lower_camel" , "Upper_camel"
```{r}
Co2_rating <- clean_names(dat = Co2_rating,case = "snake") 
glimpse(Co2_rating)
```
# rename the function
```{r}
Co2_rating <- Co2_rating %>%
  rename(model_year = model_1,
         model_type = model_3,
         n_cylinder = cylinders,
         fuel_type = fuel,
         fcons_city = fuel_consumption,
         fcons_highway = x10,
         fcons_combined = x11,
         fcons_combining_mpg = x12,
         co2_emision = co2_emissions,
         Co2_rating = co2,
         smog_rating = smog)

glimpse(Co2_rating)
```
```{r}
# see the summary of the data set
skim(Co2_rating)  
```

```{r}
view(Co2_rating)
```

# Here Transmission AM8 - This one have two values . one is type and speed or gears of the data . So split String

```{r}
Co2_rating <- Co2_rating %>%
  mutate(n_gears = as.numeric(str_extract(transmission,"[0-9]+")),
         transmission = str_extract(transmission,"[A-Z]+"))
```

# get the summary of the new variable
```{r}
Co2_rating %>%
  select(n_gears,transmission) %>%
  skim()
```

```{r}
skim(Co2_rating)
```

```{r}
# because change contentiously transmission
Co2_rating %>%
  filter(is.na(n_gears)) %>%
  view()
```

# Handling the mising values because we can't clear the data set so assume the meaning ful name
```{r}
Co2_rating <- Co2_rating %>%
  mutate(n_gears = ifelse(is.na(n_gears),-1,n_gears))
```

# Change the type and keep the unused model
```{r}
Co2_rating <- Co2_rating %>%
  mutate(transmission_type = factor(transmission),.keep = "unused")

```

```{r}
skim(Co2_rating)
```
# re allocate the column 
```{r}
Co2_rating <- Co2_rating %>%
  relocate(transmission_type,fuel)
```

# remove the view() part when we knit the rmarkdown file.
```{r}
view(Co2_rating)
```

